### 2014-03-11 src/discussion.Rnw
update

There may infact be a simple reason for this observation. Consider the Figure~\ref{fig:egmutants}.
It is a representation of the distribution of mutants along two orthogonal axes --- the
mutation operators, and program elements such as classes. For the purposes of this
explanation, assume that each classes contain about five lines, and each mutant
produced per line by each of the mutation operators are marked by a small solid circle.
The two solid vertical lines in blue and red represents two classes, one with a relatively
small number of mutants and other with large number of mutants. Further, let use use
$N_{red}$ as the number of mutants in red class, and $N_{blue}$ as the number of mutants
in blue classs, and $N_{blue} > N_{red}$ as shown in figure, and let $N$ be the total
number of mutants, and $C$ the number of classes.

To consider a concrete example, consider two classes with 4 and 2 mutants respectively.
Then -- \textbf{solve} --

>>>>

There may infact be a simple reason for this observation. Consider the Figure~\ref{fig:egmutants}.
It is a representation of the distribution of mutants along two orthogonal axes --- the
mutation operators, and program elements such as classes. For the purposes of this
explanation, assume that each classes contain equal number of lines, and each mutant
produced per line by each of the mutation operators are marked by a small solid circle.
The two solid vertical lines in blue and red represents two classes, one with a relatively
small number of mutants and other with large number of mutants. Consider that we are sampling
by class, and we are choosing all mutants for simplicity. Let $c$ be the number of classes.
Here, a mutant in red class contributes to $1/n_{red}$ to the mean of the score of the
red class, and the red class contributes $1/c$ to the total mean.  So the contribution of a
mutant in red class to the complete is $1/(c * n_{red})$. Similarly for blue class.
However, if the sampling is done on a complete project basis, then the contribution of any
mutant is $\frac{1}{\sum_{i=1}^{c} n_{i}}$, which depending on the size of the class might
be different from what it would contribute if sampling is used. To put it another way,
for any kind of sampling used based on sub elements, the units in the sample gets equal
weightage in contribution irrespective of the size of elements themselves, while if the sampling
is done on a project basis, the contribution of sub elements depends on the number of mutants
each elements produced.
